Complementary Filters Shaping Using $\mathcal{H}_\infty$ Synthesis

### 2019-10-29 poster/poster.tex
Update poster

\documentclass[%
    a0paper,%
    20pt,%
    portait,%
    margin=0mm,%
    innermargin=10mm,%
    blockverticalspace=10mm,%
    colspace=10mm,%
    subcolspace=5mm%
]{tikzposter}

@@

\author{Dehaeze Thomas, Verma Mohit and Collette Christophe}
\date{2019-11-06}
\title{Complementary Filters Shaping Using \scalebox{2}{$\mathcal{H}_\infty$} Synthesis}
\institute{}

@@

\maketitle[%
    roundedcorners=2,
    linewidth=2mm,
    innersep=10mm,
    titletotopverticalspace=10mm,
    titletoblockverticalspace=10mm]

@@

\begin{columns}
\column{0.5}
\block[]{Introduction}{\input{introduction.tex}}
\block[]{Complementary Filters Requirements}{\input{requirements.tex}}

>>>>

\documentclass[%
    a1paper,%
    17pt,%
    portait,%
    margin=0mm,%
    innermargin=5mm,%
    blockverticalspace=5mm,%
    colspace=5mm,%
    subcolspace=2mm%
]{tikzposter}

\usetitlestyle[]{Wave}

@@

\author[1,2]{Dehaeze Thomas}
\author[1,3]{Verma Mohit}
\author[1,3]{Collette Christophe}
\affil[1]{Precision Mechatronics Laboratory, A\&M Department, University of Liege, Belgium}
\affil[2]{European Synchrotron Radiation Facility, Grenoble, France}
\affil[3]{BEAMS Department, Free University of Brussels, Belgium}

\date{2019-11-06}
\title{Complementary Filters Shaping Using $\mathcal{H}_\infty$ Synthesis}
\institute{}

@@

\maketitle[%
    roundedcorners=2,
    linewidth=2mm,
    innersep=5mm,
    titletotopverticalspace=10mm,
    titletoblockverticalspace=10mm]

@@

\begin{columns}
\column{0.5}
% \block[]{Introduction}{\input{introduction.tex}}
\block[]{Sensor Fusion Architecture}{\input{architecture.tex}}
\block[]{Complementary Filters Requirements}{\input{requirements.tex}}

### 2019-10-29 poster/requirements.tex
Update poster

\begin{tikzfigure}[Sensor fusion architecture]
  \label{fig:fusion_super_sensor}
  \centering
  \includegraphics[scale=1.8]{figs/fusion_super_sensor.pdf}
\end{tikzfigure}

\begin{tikzfigure}[Sensor fusion architecture with sensor dynamics uncertainty]
  \label{fig:sensor_fusion_dynamic_uncertainty}
  \centering
  \includegraphics[scale=1.8]{figs/sensor_fusion_dynamic_uncertainty.pdf}
\end{tikzfigure}

\begin{tikzfigure}[Uncertainty set of the super sensor dynamics]
  \label{fig:uncertainty_set_super_sensor}
  \centering
  \includegraphics[scale=1.8]{figs/uncertainty_set_super_sensor.pdf}
\end{tikzfigure}

>>>>

%%% Local Variables:
%%% TeX-master: "poster"
%%% End:

\begin{minipage}[t]{0.5\linewidth}
  \begin{center}
    {\Large \textbf{Noise Property}}
  \end{center}
\end{minipage}\hfill
\begin{minipage}[t]{0.5\linewidth}
  \begin{center}
    {\Large \textbf{Dynamical Uncertainty}}
  \end{center}
\end{minipage}\hfill

\hspace*{-10pt}\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Sensor fusion architecture]
    \centering
    \label{fig:fusion_super_sensor}
    \includegraphics[height=6cm]{figs/fusion_super_sensor.pdf}
  \end{tikzfigure}

  First suppose \textbf{known sensor dynamics}, such that the dynamics can be
  inverted:
  \[ G_1(s) = G_2(s) = 1 \]

  The estimate $\hat{x}$ is then:
  \[ \tcmbox{\hat{x} = x + H_1 n_1 + H_2 n_2} \]

  The signal $x$ is kept \textbf{undistorted} while the noises $n_1$ and $n_2$ are \textbf{filtered out by the complementary filters}.\newline

  Estimate error $\delta x$:
  \[ \delta x \triangleq \hat{x} - x = H_1 n_1 + H_2 n_2 \]

  PSD of the super sensor noise:
  \[ \tcmbox{\Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} +
      \left|H_2\right|^2 \Phi_{n_2}} \]
\end{minipage}\hspace{20pt}
\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Fusion of sensors with dynamics uncertainty]
    \centering
    \label{fig:sensor_fusion_dynamic_uncertainty}
    \includegraphics[height=6cm]{figs/sensor_fusion_dynamic_uncertainty.pdf}
  \end{tikzfigure}

  Sensor dynamic uncertainty is represented by \textbf{multiplicative input uncertainty}:
  \[ \begin{aligned}
      G_i^\prime(s) = G_i(s) [1 + & w_i(s)\Delta_i(s)], \\
      &\forall\Delta_i, \|\Delta_i\|_\infty < 1
    \end{aligned} \]

  The super sensor dynamics is:
  \[ \tcmbox{\frac{\hat{x}}{x} = 1 + w_1 H_1 \Delta_1 + w_2 H_2 \Delta_2} \]

  The super sensor dynamic uncertainty is represented in the complex plane in
  Fig.~\ref{fig:uncertainty_set_super_sensor}.

  \begin{tikzfigure}[Uncertainty set of the super sensor dynamics]
    \label{fig:uncertainty_set_super_sensor}
    \centering
    \includegraphics[width=0.8\linewidth]{figs/uncertainty_set_super_sensor.pdf}
  \end{tikzfigure}
\end{minipage}
\vspace{1em}
\sepline

As shown in the analysis above, \textbf{the performance and robustness of the sensor fusion architecture depends on the complementary filters norms}.
Therefore, the development of a synthesis method of complementary filters that allows the shaping of their norm is necessary.
